Imputing missing SDs

### 2023-01-06 Working Rmds/impute_missing_sds.Rmd
Fix error in computing sd vs. mean relation, and implement the fixed result when imputing missing SDs.

By chemical, species, reference, medium, dose group, and time point: calculate mean and standard deviation.

@@

cvt_summarized <- cvt[N_Subjects==1,
                      .(meanval = mean(Value, na.rm = TRUE),
                        sdvals = sd(Value, na.rm = TRUE),
                        n = .N),
                      by = .(Reference,
                             DTXSID,
                             Media,
                             Dose,
                             Time)]
```

@@

ggplot(cvt_summarized,
       aes(x = meanval,
           y = sdvals)) +
  geom_point(aes(color = n)) +
  geom_abline(intercept = 0, slope =1 , linetype = 2) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  scale_x_log10() +
  scale_y_log10() +
  scale_color_viridis_c(trans = "log10",
                        name = "# subjects") +
  annotation_logticks(sides = "bl") +
  xlab("Mean conc., mg/kg") +
  ylab("Sample std dev conc., mg/kg") +
  ggtitle("Mean vs. SD for N=1 data\ngrouped by chemical, reference, medium, dose, timepoint") 
```

@@

cvt_summarized[!is.finite(log10_sdvals), log10_sdvals := NA_real_]
cvt_summarized[!is.finite(log10_meanval), log10_meanval := NA_real_]
```

```{r}
summary(lm(log10_sdvals ~ log10_meanval,
           data = cvt_summarized,
           na.action = na.omit))
```

@@

$$ \log \textrm{SD} = -0.517 + 0.953 \log \textrm{Mean} $$

@@

$$ \log_{10} \textrm{SD} = -0.517 + \log_{10} \textrm{Mean}^{0.953} $$
$$ \log_{10} \textrm{SD} = \log_{10}{ \left( 10^{-0.517} \times \textrm{Mean}^{0.953} \right)}  $$

@@

$$ \textrm{SD} = 10^{-0.517} \times \textrm{Mean}^{0.953} $$

@@

$$ \textrm{SD} = 0.3 \times \textrm{Mean}^{0.953} $$

>>>>

By chemical, species, reference, medium, dose group, route, and time point: calculate mean and standard deviation.

@@

cvt_summarized <- cvt[N_Subjects==1,
                      .(meanval = mean(Value, na.rm = TRUE),
                        sdvals = sd(Value, na.rm = TRUE),
                        n = .N),
                      by = .(Reference,
                             DTXSID,
                             Species,
                             Media,
                             Route,
                             Dose,
                             Time)]
```

@@

ggplot(cvt_summarized,
       aes(x = meanval,
           y = sdvals)) +
  geom_point(aes(color = n)) +
  geom_abline(intercept = 0, slope =1 , linetype = 2) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  scale_x_log10() +
  scale_y_log10() +
  scale_color_viridis_c(trans = "log10",
                        name = "# subjects") +
  annotation_logticks(sides = "bl") +
  xlab("Mean conc., mg/kg") +
  ylab("Sample std dev conc., mg/kg") +
  ggtitle("Mean vs. SD for N=1 data") 
```

@@

cvt_summarized[!is.finite(log10_sdvals), log10_sdvals := NA_real_]
cvt_summarized[!is.finite(log10_meanval), log10_meanval := NA_real_]

summary(lm(log10_sdvals ~ log10_meanval,
           data = cvt_summarized,
           na.action = na.omit))
```

@@

$$ \log \textrm{SD} = -0.555 + 0.939 \log \textrm{Mean} $$

@@

$$ \log_{10} \textrm{SD} = -0.555 + \log_{10} \textrm{Mean}^{0.939} $$
$$ \log_{10} \textrm{SD} = \log_{10}{ \left( 10^{-0.555} \times \textrm{Mean}^{0.939} \right)}  $$

@@

$$ \textrm{SD} = 10^{-0.555} \times \textrm{Mean}^{0.939} $$

@@

$$ \textrm{SD} = 0.278 \times \textrm{Mean}^{0.939} $$
